What We Eval in the Shadows

### 2021-04-13 analysis/provenance.Rmd
Changes
Fixing environments

>>>>

# Another classification

```{r}
string_exprs <- E_prov %>% filter(!is.na(parsed))
nb_string_expr_sites <- n_distinct(string_exprs$src_ref)

constructed_exprs <- bind_rows(not_parsed_exprs, other_langs) %>% anti_join(match_call_exprs)
nb_constructed_expr_sites <- n_distinct(constructed_exprs$src_ref)

unknown_prov_exprs <- E_prov %>% anti_join(string_exprs) %>% anti_join(constructed_exprs) %>% anti_join(match_call_exprs)
nb_unknown_prov_exprs_sites <- n_distinct(unknown_prov_exprs$src_ref)

overview_table(
  r("nb constructed sites", nb_constructed_expr_sites),
  r("nb constructed site percent", ratio(nb_constructed_expr_sites, nb_call_sites)),
  r("nb string sites", nb_string_expr_sites),
  r("nb string site percent", ratio(nb_string_expr_sites, nb_call_sites)),
  r("nb unknown sites", nb_unknown_prov_exprs_sites),
  r("nb unknown site percent", ratio(nb_unknown_prov_exprs_sites, nb_call_sites)),
) 
# last category is match.call but we have it elsewhere
```

```{r}
duration <- difftime(Sys.time(), now)
```

Notebook execution was `r duration` `r units(duration)`.

### 2021-04-13 paper/main.tex
Fixing environments

\begin{table}[h]\small
\begin{tabular}{r|r|r} \hline
Origin  & \#sites & \%sites \\\hline
Promise & \packageNbOtherLangsSites & \packageOtherLangsSitePercent \\ \hline
Parse & ?& ?\\ \hline
\c{match.call} &  \packageNbMatchCallExprsSites & \packageMatchCallExprsSitePercent  \\\hline
Constructed & ? &?  \\\hline
\end{tabular}
\caption{Provenance}\label{tab:provenance}
\end{table}

>>>>

\begin{table}[h]\small
\begin{tabular}{r|r|r} \hline
Origin  & \#sites & \%sites \\\hline
Constructed & \packageNbConstructedSites & \packageNbConstructedSitePercent \\ \hline
String & \packageNbStringSites & \packageNbStringSitePercent \\ \hline
Reflection &  \packageNbMatchCallExprsSites & \packageMatchCallExprsSitePercent  \\\hline
Other & \packageNbUnknownSites & \packageNbUnknownSitePercent \\\hline
\end{tabular}
\caption{Provenance}\label{tab:provenance}
\end{table}
